\documentclass[margin,line]{res}

\usepackage{hyperref}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
% if using pdflatex:
%\setlength{\pdfpagewidth}{\paperwidth}
%\setlength{\pdfpageheight}{\paperheight} 

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Jamie Hayes \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3in}p{4in}}
{\it Email:}    \url{j.hayes@cs.ucl.ac.uk} 
& {\it WWW:} \url{https://jhayes14.github.io}\\      
   
\end{tabular}

\section{\sc Experience}

{\bf Google DeepMind}, London, UK

\vspace{-.3cm}
{\em Research Scientist} \hfill {\bf May, 2020 - }

Research into verification and robustness guarantees in machine learning.

{\bf Google DeepMind}, London, UK

\vspace{-.3cm}
{\em Internship} \hfill {\bf May, 2019 - September, 2019}

Research into zero-bit watermarking applications in machine learning.

{\bf Google Research}, Mountain View, CA, USA

\vspace{-.3cm}
{\em Internship} \hfill {\bf July, 2018 - September, 2018}

Research into generative and adversarial machine learning. Developed new techniques for unsupervised style transfer,
and new probabilistic conditioning methods for generative models.

{\bf Microsoft Research}, Cambridge, UK

\vspace{-.3cm}
{\em Internship} \hfill {\bf February, 2018 - May, 2018}

Research into security and privacy attacks and defenses in multi-party machine learning.

{\bf Naval Research Laboratory}, Washington, DC, USA

\vspace{-.3cm}
{\em Internship} \hfill {\bf August, 2017 - October, 2017}

Research into adversarial machine learning and network traffic analysis. Proposed a project on using machine learning
techniques for performing privacy-preserving experiments into live traffic analysis attacks on Tor.

{\bf Government Digital Services}, London, UK

\vspace{-.3cm}
{\em Intern for the SecOps team} \hfill {\bf March,
  2017 - July, 2017}

I developed and implemented a privacy-preserving machine learning pipeline to aid threat analysis
and improve Transaction Monitoring (TxM) on the GOV.UK Verify system.

{\bf University of Manchester}, Manchester, UK

\vspace{-.3cm}
{\em Network Technician} \hfill {\bf September, 2011 - March, 2013}

Maintenance of the internal University network that provided a
connection to over 10,000 students. Duties included server
maintenance, switch configurations, some SDN programming.


\section{\sc Education}
{\bf Dept. of Computer Science, University College London}, UK\\
{\bf Sep. 2014 - Present} - Ph.D. candidate\\
Privacy, Security and Machine Learning\\
Advisor:  Prof. George Danezis\\
Second Advisor: Prof. Thore Graepel

{\bf Computer Laboratory, University of Cambridge}, UK\\
{\bf Sep. 2013 - Apr. 2014} - Researcher\\
Parameterized Computational Complexity of the Graph Isomorphism Problem\\
Advisor: Prof. Anuj Dawar

{\bf Dept. of Mathematics, University of Manchester}, UK\\
%{\em Department of Mathematics and Statistics} 
{\bf Sep. 2007 - Jun. 2011} - Master of Mathematics\\
First Class Grade (graduated 4th out of a class of 76)\\
Advisor: Prof. Richard Sharp


\section{\sc Honors and Awards} 


%Alan Turing Institute Summer Research Grant, 2016 (Refused)

%\vspace*{-2.5mm}

NeurIPS 2018 Student Travel Award\newline

\vspace*{-3mm}

NeurIPS 2017 Student Travel Award\newline

\vspace*{-3mm}

Google Phd Fellowship in Machine Learning (2017-2020)\newline

\vspace*{-3mm}

\noindent Invited to Google PhD Summit in Security (2016) and Machine
Learning (2017)\newline

\vspace*{-3mm}

Academic Center of Excellence Studentship, 2014\newline

\vspace*{-3mm}

Engineering and Physical Sciences Research Council (EPSRC) Doctoral
Training Studentship, 2013


\section{\sc Research}

Extensions and limitations of randomized smoothing for robustness guarantees\\
J Hayes 06-2020 CVPR (workshop track)  

A framework for robustness certification of smoothed classifiers using f-divergences\\
K Dvijotham, J Hayes, B Balle, Z Kolter, C Qin, A Gyorgy, K Xiao, S Gowal, P Kohli 05-2020 ICLR

Towards transformation-resilient provenance detection of digital media\\
J Hayes, K Dvijotham, Y Chen, S Dieleman, P Kohli, N Casagrande 09-2019  

LOGAN: Membership inference attacks against generative models\\
J Hayes, L Melis, G Danezis, E De Cristofaro 07-2019 PETS  

A note on hyperparameters in black-box adversarial examples\\
J Hayes 12-2018  

Evading classifiers in discrete domains with provable optimality guarantees\\
B Kulynych, J Hayes, N Samarin, C Troncoso 12-2018 NeurIPS (workshop track)  

Contamination attacks in multi-party machine learning\\
J Hayes, O Ohrimenko 12-2018 NeurIPS 

On visible adversarial perturbations \& digital watermarking\\
J Hayes 06-2018 CVPR (workshop track) 

Learning universal adversarial perturbations with generative models\\
J Hayes 05-2018 DLS (IEEE S\&P workshop)  

Generating steganographic images via adversarial training\\
J Hayes, G Danezis 12-2017 NeurIPS  

AnNotify: A private notification service\\
A Piotrowska, J Hayes, N Gelernter, G Danezis, A Herzberg 10-2017 WPES  

The Loopix anonymity system\\
A Piotrowska, J Hayes, T Elahi, S Meiser, G Danezis 08-2017 USENIX Security  

Website fingerprinting defenses at the application layer\\
G Cherubin, J Hayes, M Juarez 07-2017 PETS  

TASP: Towards anonymity sets that persist\\
J Hayes, C Troncoso, G Danezis 10-2016 WPES  

\emph{k}-fingerprinting: a robust scalable website fingerprinting technique\\
J Hayes, G Danezis 08-2016 USENIX Security  

Traffic confirmation attacks despite noise\\
J Hayes 02-2016 NDSS (workshop track)  

Guard sets for onion routing\\
J Hayes 07-2015 PETS  

An introduction to the dynamics of real and complex quadratic polynomials\\
J Hayes 07-2011  

\section{\sc Presentations}

On visible adversarial perturbations \& digital watermarking,
CVPR Workshop track

Learning universal adversarial perturbations with generative models,
DLS (IEEE S\&P Workshop)

Invited talk on Adversarial Machine Learning\\
IBM, IBM Thomas J. Watson Research Center

Invited talk on Network Traffic Analysis\\
UK Gov

TASP: Towards Anonymity Sets that Persist\\
WPES (Workshop of CCS) 

\emph{k}-fingerprinting: a Robust Scalable Website Fingerprinting
Technique\\
USENIX Security 

Traffic Confirmation Attacks Despite Noise\\
Understanding and Enhancing Online Privacy (Workshop of NDSS)

Guard Sets for Onion Routing\\
PETS 

Guard Sets for Onion Routing\\
University College London Information Security Seminar

Secure Sets in Graphs\\
Programming, Logic, and Semantics Reading Group, Computer Lab, University of Cambridge


\section{\sc Program committee member}

AAAI 2020

CVPR 2020

NeurIPS 2019, 2020

ICLR 2020 Workshop on "Towards Trustworthy ML: Rethinking Security and Privacy for ML"

PrivateNLP'20 (WSDM 2020 Workshop on Privacy and Natural Language Processing)

ICML 2019

 PPML19 (Privacy-Preserving Machine Learning - CCS 2019 Workshop)

Privacy Enhancing Technologies Symposium 2018, 2019, 2020, 2021

NeurIPS 2018 Workshop on Security in Machine Learning

(External) CCS, 2017

(External) NDSS, 2016

(External) IEEE Symposium on Security and Privacy, 2016

Transactions on Information Forensics \& Security

Transactions on Pattern Analysis and Machine Intelligence

\section{\sc Teaching}

Advisor (along with George Danezis) for Hugo Picq's MSc Thesis, `Understanding and Scaling a Robust Neural Network', 2019

Advisor for Axel Goetz's MSc Thesis, `Evaluating the use of Deep Learning for Website Fingerprinting', 2017


\section{\sc Skills} 
\textbf{Knowledge of}:\\
Python \textbullet{} Go \textbullet{} Shell \textbullet{} \LaTeX \textbullet{}
Unix/Linux \textbullet{} Vim \textbullet{} Machine Learning
(TensorFlow, PyTorch, JAX, SKLearn)  

\textbf{Exposure to}:\\
C++ \textbullet{} Haskell \textbullet{} JavaScript \textbullet{} C \textbullet{} SQL \textbullet{} HTML
\textbullet{} CSS \textbullet{} Git

\section{\sc Code and Side Projects}

Public code available at \url{https://github.com/jhayes14}, code for
private projects available on request. 

\section{\sc References} 

Please inform me if references are to be contacted.

\textbf{George Danezis}\newline
Reader in Security and Privacy Engineering (Professor) \newline
Email: g.danezis[at]ucl.ac.uk \newline
University College London,\newline
Dept. of Computer Science,\newline
Gower Street, London WC1E 6BT, U.K. \newline

\textbf{Louise Walker}\newline
Reader in Mathematics \newline
Email: Louise.Walker[at]manchester.ac.uk \newline
Room 2.243, Alan Turing Building \newline
School of Mathematics,\newline
University of Manchester \newline
Oxford Road, Manchester M13 9PL, UK \newline


\end{resume}
\end{document}



